Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-09 manuscript/manuscript.Rmd
mini

Since our state and observation spaces are continuous, we will focus on deep reinforcement learning throughout this paper.
Specifically, we parametrize $\pi$ using a XXXX neural network and use the *proximal policy optimization (PPO)* algorithm to optimize $\pi$.
Within the RL literature there is a wealth of algorithms from which to choose from, each with its pros and cons.
Here we have focused on a single one of these for the sake of particularity---to draw a clear comparison between the RL-based and the classical fishery management approaches.
In practice, further improvements can be expected by a careful selection of the optimization algorithm.

>>>>

Since our state and observation spaces are continuous, we will focus on deep reinforcement learning throughout this paper.
Specifically, we parametrize $\pi$ using a neural network with two hidden layers of 64 neurons.

We use the *proximal policy optimization (PPO)* algorithm to optimize $\pi$.
Within the RL literature there is a wealth of algorithms from which to choose from, each with its pros and cons.
Here we have focused on a single one of these for the sake of particularity---to draw a clear comparison between the RL-based and the classical fishery management approaches.
In practice, further improvements can be expected by a careful selection of the optimization algorithm.
